%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[margin=0.42in]{geometry}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%% RESUME STARTS HERE %%%%%%%
\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Aditya Harshavardhan} \\ \vspace{1pt}
    \small
    \href{tel:6082091711}{(608)-209-1711} $|$
    \href{mailto:harshavardha@wisc.edu}{harshavardha@wisc.edu} $|$
    \href{https://linkedin.com/in/aditya-harshavardhan11}{linkedin.com/in/aditya-harshavardhan11} $|$
    \href{https://github.com/aditya-harsh11}{github.com/aditya-harsh11}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
        {University of Wisconsin-Madison}{Expected Graduation: May 2028}
        {Bachelor of Science, Computer Science}{\textbf{GPA: 4.0/4.0}}
        \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Data Structures \& Algorithms, Object-Oriented Programming, Computer Architecture, Discrete Mathematics, Calculus}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
        {Perception \& Infrastructure Engineer}{February 2026 -- Present}
        {Wisconsin Autonomous}{Madison, WI}
    \resumeItemListStart
        \resumeItem{Optimized a lane segmentation model to sustain 60 FPS inference and built a 3D geometry-based stop bar detection algorithm for precise vehicle positioning at intersections.}
        \resumeItem{Developed ego-trajectory estimation and Bird's Eye View obstacle mapping from RGB and depth sequences, using color-based detection to classify dynamic and static objects in real time.}
        \resumeItem{Integrated legacy V2X modules into a new codebase and built a UDP-based simulation node for real-time vehicle beacon processing and nearest-neighbor tracking.}
    \resumeItemListEnd

    \resumeSubheading
        {Technical Scholar}{March 2026 -- Present}
        {Wisconsin AI Safety Initiative}{Madison, WI}
    \resumeItemListStart
        \resumeItem{Completed ARENA and BlueDot based curricula, implementing core deep learning architectures from scratch and studying deceptive alignment, reward misspecification, adversarial evaluations, interpretability, and AI control.}
        \resumeItem{Analyzed 8+ AI safety research papers spanning mechanistic interpretability, scalable oversight, alignment, and evals as part of a structured cohort program.}
    \resumeItemListEnd

    \resumeSubheading
        {Data Engineer}{February 2026 -- May 2026}
        {Biokind Analytics}{Madison, WI}
    \resumeItemListStart
        \resumeItem{Analyzed 92,000+ attendance and 33,000+ membership records across multiple years to build disengagement profiles for 10,000+ children at Boys \& Girls Clubs of Dane County.}
        \resumeItem{Built a 3-factor risk score model that identified high-risk youth subgroups with disengagement rates above 78\%, enabling organizational leadership to shift from reactive tracking to proactive early intervention.}
        \resumeItem{Modeled 4+ years of time-series attendance data to find seasonal dropout patterns and behavioral consistency, delivering stakeholder-ready visualizations to organizational leadership.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- PROJECTS -----------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{ArcFlow} $|$ \emph{Next.js, React Flow, FastAPI, Python, Electron, ONNX, Nexa SDK}}{}
    \resumeItemListStart
        \resumeItem{Won 1st Place at a Qualcomm-sponsored hackathon (MadData 26); selected to present at the 2026 Qualcomm University Developer Symposium and UW--Madison N+1 Symposium.}
        \resumeItem{Built a node-based AI pipeline editor for designing multimodal workflows via drag-and-drop or natural language prompts, streaming real-time video and audio between a Next.js/React Flow frontend and FastAPI backend.}
        \resumeItem{Deployed YOLOv8, YamNet, and OmniNeural-4B to the Qualcomm NPU via ONNX Runtime and Nexa SDK, enabling fully on-device inference with no external API calls or internet dependency.}
    \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Unsilenced} $|$ \emph{Next.js, Flask, TypeScript, MediaPipe, Face API, Fish Audio}}{}
    \resumeItemListStart
        \resumeItem{1st Place Winner, Fish Audio Track at the Midwest's largest collegiate hackathon (MadHacks 2025); built a hands-free AAC tool to restore vocal identity for non-verbal users.}
        \resumeItem{Engineered a 30+ FPS nose-tracking interface using MediaPipe Face Mesh and a 2,800+ word autocomplete dictionary, reducing sentence generation time by over 50\% compared to existing synthesizers.}
        \resumeItem{Achieved 85\% emotion detection accuracy by integrating Face API CNNs with Fish Audio via a Flask proxy, dynamically matching synthetic voice tone and pitch to the user's facial expressions in real time.}
    \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Centralized Event Dashboard} $|$ \emph{TypeScript, SvelteKit, Python, Flask, SQLite, AWS EC2, Gemini}}{}
    \resumeItemListStart
        \resumeItem{Built a campus event dashboard with SvelteKit and TypeScript, consolidating 50+ events from emails, Discord, and flyers into a single searchable calendar for 1000+ university students.}
        \resumeItem{Architected an automated data ingestion pipeline using Python and IMAP that monitors a shared inbox 24/7, processing 70+ emails/week through Google Gemini for structured extraction and database population.}
        \resumeItem{Developed a REST API with Flask and SQLite to manage event records and a Discord bot serving 10+ channels for real-time event notifications, both deployed on AWS EC2.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- SKILLS -----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
    \item{
        \textbf{Languages:} Python, JavaScript, Java, SQL, Dart, HTML, CSS \\
        \textbf{Frameworks \& Libraries (SWE):} React, Next.js, FastAPI, Flask, Flutter, JavaFX, JUnit \\
        \textbf{Frameworks \& Libraries (AI/ML):} PyTorch, NumPy, Pandas, Matplotlib \\
        \textbf{Developer Tools:} Git, GitHub, Docker, Firebase \\
    }
}
\end{itemize}

\end{document}
